\textbf{Effective application of machine learning to a microbiome-based classification problem}

### 2020-01-21 submission/manuscript.tex
updates for rebuttal

ML models can be used to increase our understanding of the variation in
the structure of existing data and in making predictions about new data.
Researchers have used ML models to diagnose and understand the
ecological basis of diseases such as liver cirrhosis, colorectal cancer,
inflammatory bowel diseases, obesity, and type 2 diabetes (2--19). The
task of diagnosing an individual relies on a rigorously validated model.
However, there are common methodological and reporting problems that
arise when applying ML to such data, that need to be addressed for the
field to progress. These problems include a lack of transparency in
which methods are used and how these methods are implemented; evaluating
models without separate held-out test data; unreported variation between
the predictive performance on different folds of cross-validation; and
unreported variation between cross-validation and testing performances.
Though the microbiome field is making progress to avoid some of these
pitfalls including validating their models on independent datasets (8,
19, 20) and introducing ways to better use ML tools (21--24), more work
is needed to improve reproducibility further and minimize overestimating
for model performance.

@@

In this study, we provided steps toward standardization of machine
learning methods for microbiome studies which are often poorly
documented and executed. To showcase a rigorous ML pipeline and to shed
light on how ML model selection can affect modeling results, we
performed an empirical analysis comparing seven modeling approaches with
the same dataset and pipeline. We built three linear models with
different forms of regularization: L2-regularized logistic regression
and L1 and L2-regularized support vector machines (SVM) with a linear
kernel. We also trained four non-linear models: SVM with radial basis
function kernel, a decision tree, random forest, and gradient boosted
trees. We compared their predictive performance, interpretability, and
training time. To demonstrate the performance of these modeling
approaches and our pipeline on a case study, we used a data from a
previously published study that sought to classify individuals as having
healthy colons or colonic lesions based on the 16S rRNA gene sequences
collected from fecal samples (4). This dataset was selected because it
is a relatively large collection of individuals (N=490) connected to a
clinically significant disease where there is ample evidence that the
disease is driven by variation in the microbiome (2, 4, 5, 32). With
this dataset, we developed an ML pipeline that can be used in many
different scenarios for training and evaluating models. This framework
can be easily applied to other host-associated and environmental
microbiome datasets. We hope that this study \ldots{}

@@

First, we randomly split the data into training and test sets so that
the training set consisted of 80\% of the full dataset, while the test
set was composed of the remaining 20\% {[}Figure 1{]}. To maintain the
distribution of controls and cases found in the full dataset, we
performed stratified splits. For example, our full dataset included 490
individuals. Of these, 261 had healthy colons (53\%) and 229 had a
screen relevant neoplasia (SRN; 46.7\%). A training set included 393
individuals, of which 209 had an SRN (53\%), while the test set was
composed of 97 individuals, of which 52 had an SRN (54\%). The training
data were used to build and select the models, and the test set was used
for evaluating the model.

We trained seven different models using the training data {[}Table 1{]}.
We focused on different classification algorithms and regularization
methods. Regularization helps to prevent overfitting by penalizing a
model that fits the training data too well (33). For regularized
logistic regression and SVM with a linear kernel, we used
L2-regularization to keep all potentially important features. For
comparison, we also trained an L1-regularized SVM with a linear kernel.
L1-regularization on microbiome data led to a sparser solution (i.e.,
forced many coefficients to zero). To explore the potential for
non-linear relationships among features to improve classification, we
trained tree-based models including, a decision tree, a random forest,
and gradient boosted trees (XGBoost) and an SVM with a non-linear
kernel.

@@

\textbf{Interpretation of each ML model.} Interpretability is related to
the degree to which humans can understand the reasons behind a model
prediction (34--36). Because we often use ML models not just to predict
a health outcome, but also to identify potential biomarkers for disease,
model interpretation becomes crucial for microbiome studies. ML models
often decrease in interpretability as they increase in complexity. In
this study, we used two methods to help interpret our models.

First, we interpreted the feature importance of the linear models (L1
and L2-regularized SVM with linear kernel and L2-regularized logistic
regression) using the median rank of absolute feature weights for each
OTU {[}Figure 3{]}. We also reviewed the signs of feature weights to
determine whether an OTU was associated with classifying a subject as
being healthy or having an SRN. It was encouraging that many of the
highest-ranked OTUs were shared across these three models (e.g., OTUs
50, 426, 609, 822, 1239). The benefit of this approach was that the
results of the analysis were based on the trained model parameters and
provided information regarding the sign and magnitude of the impact of
each OTU. However, this approach is limited to linear models or models
with prespecified interaction terms.

Second, to analyze non-linear models, we interpreted the feature
importance using permutation importance (37). Whereas the absolute
feature weights were determined from the trained models, here we
measured importance using the held-out test data. Permutation importance
analysis is a post hoc explanation of the model, in which we randomly
permuted groups of perfectly correlated features together and other
features individually across the two groups in the held-out test data.
We then calculated how much the predictive performance of the model
(i.e., testing AUROC values) decreased when each OTU or group of OTUs
was randomly permuted. We ranked the OTUs based on how much the median
testing AUROC decreased when it was permuted; the OTU with the largest
decrease ranked highest {[}Figure 4{]}. Among the twenty OTUs with the
largest impact, there was only one OTU (OTU 822) that was shared among
all of the models; however, we found three OTUs (OTUs 58, 110, 367) that
were important in each of the tree-based models. Similarly, the random
forest and XGBoost models shared four of the most important OTUs (OTUs
2, 12, 361, 477). Permutation analysis results also revealed that with
the exception of the decision tree model, removal of any individual OTU
had minimal impact on model performance. For example, if OTU 367 was
permuted across the samples in the decision tree model, the median AUROC
dropped from 0.601 to 0.525. In contrast, if the same OTU was permuted
in the random forest model, the AUROC only dropped from 0.695 to 0.680,
which indicated high degree of collinearity in the dataset. Permutation
analysis allowed us to gauge the importance of each OTU in non-linear
models and partially account for collinearity by grouping correlated
OTUs to determine their impact as a group.

To further highlight the differences between the two interpretation
methods, we used permutation importance to interpret the linear models
{[}Figure S5{]}. When we analyzed the L1-regularized SVM with linear
kernel model using feature rankings based on weights {[}Figure 3{]} and
permutation importance {[}Figure S5{]}, 17 of the 20 top OTUs (e.g., OTU
609, 822, 1239) were deemed important by both interpretation methods.
Similarly, for the L2-regularized SVM and L2-regularized logistic
regression, 9 and 12 OTUs, respectively, were shared among the two
interpretation methods. These results indicate that both methods are
consistent in selecting the most important OTUs.

@@

We highlighted the importance of model interpretation to gain greater
biological insights into microbiota-associated diseases. In this study,
we showcased two different interpretation methods: ranking each OTU by
(i) their absolute weights in the trained models and (ii) their impact
on the predictive performance based on permutation importance.
Human-associated microbial communities have complex correlation
structures that create collinearity in the datasets. This can hinder our
ability to reliably interpret models because the feature weights of
correlated OTUs are influenced by one another (38). To capture all
important features, once we identify highly ranked OTUs, we should
review their relationships with other OTUs. These relationships will
help us generate new hypotheses about the ecology of the disease and
test them with follow-up experiments. When we used permutation
importance, we partially accounted for collinearity by grouping
correlated OTUs to determine their impact as a group. We grouped OTUs
that had a perfect correlation with each other; however, we could reduce
the correlation threshold to further investigate the relationships among
correlated features. It is important to know the correlation structures
of the data to avoid misinterpreting the models. This is likely to be a
particular problem with shotgun metagenomic datasets where collinearity
will be more pronounced due to many genes being correlated with one
another because they come from the same chromosome. To identify the true
underlying microbial factors of a disease, it is crucial to follow up on
any correlation analyses with further hypothesis testing and
experimentation for biological validation.

@@

\hypertarget{ref-Ng:2004:FSL:1015330.1015435}{}
33. \textbf{Ng AY}. 2004. Feature selection, l1 vs. l2 regularization,
and rotational invariance, pp. 78. \emph{In} Proceedings of the
twenty-first international conference on machine learning. ACM, New
York, NY, USA.

\hypertarget{ref-miller_explanation_2017}{}
34. \textbf{Miller T}. 2017. Explanation in artificial intelligence:
Insights from the social sciences. arXiv:170607269 {[}cs{]}.

\hypertarget{ref-ribeiro_why_2016}{}
35. \textbf{Ribeiro MT}, \textbf{Singh S}, \textbf{Guestrin C}. 2016.
``Why should i trust you?'': Explaining the predictions of any
classifier. arXiv:160204938 {[}cs, stat{]}.

\hypertarget{ref-nori_interpretml:_2019}{}
36. \textbf{Nori H}, \textbf{Jenkins S}, \textbf{Koch P},
\textbf{Caruana R}. 2019. InterpretML: A unified framework for machine
learning interpretability. arXiv:190909223 {[}cs, stat{]}.

\hypertarget{ref-10.1093ux2fbioinformaticsux2fbtq134}{}
37. \textbf{Altmann A}, \textbf{Toloşi L}, \textbf{Sander O},
\textbf{Lengauer T}. 2010. Permutation importance: a corrected feature
importance measure. Bioinformatics \textbf{26}:1340--1347.
doi:\href{https://doi.org/10.1093/bioinformatics/btq134}{10.1093/bioinformatics/btq134}.

\hypertarget{ref-dormann_collinearity:_2013}{}
38. \textbf{Dormann CF}, \textbf{Elith J}, \textbf{Bacher S},
\textbf{Buchmann C}, \textbf{Carl G}, \textbf{Carré G}, \textbf{Marquéz
JRG}, \textbf{Gruber B}, \textbf{Lafourcade B}, \textbf{Leitão PJ},
\textbf{Münkemüller T}, \textbf{McClean C}, \textbf{Osborne PE},
\textbf{Reineking B}, \textbf{Schröder B}, \textbf{Skidmore AK},
\textbf{Zurell D}, \textbf{Lautenbach S}. 2013. Collinearity: A review
of methods to deal with it and a simulation study evaluating their
performance. Ecography \textbf{36}:27--46.
doi:\href{https://doi.org/10.1111/j.1600-0587.2012.07348.x}{10.1111/j.1600-0587.2012.07348.x}.

@@

\textbf{Figure 4. Interpretation of the non-linear ML models.} (A) SVM
with radial basis kernel, (B) decision tree, (C) random forest, and (D)
XGBoost feature importances were explained using permutation importance
on the held-out test data set. The gray rectangle and the dashed line
show the IQR range and median of the base testing AUROC without any
permutation. The 20 OTUs that caused the largest decrease in the AUROC
when permuted are reported here. The colors of the box plots represent
the OTUs that were shared among the different models; yellow were OTUs
that were shared among all the non-linear models, salmon were OTUs that
were shared among the tree-based models, green were the OTUs shared
among SVM with radial basis kernel, decision tree and XGBoost, pink were
the OTUs shared among SVM with radial basis kernel and XGBoost only, red
were the OTUs shared among random forest and XGBoost only and blue were
the OTUs shared among decision tree and random forest only. For all of
the tree-based models, a \emph{Peptostreptococcus} species (OTU00367)
had the largest impact on predictive performance. \newpage
\includegraphics{Figure_5.png}

@@

\textbf{Figure S3. Histogram of AUROC differences between L2-regularized
logistic regression and random forest for each of the hundred
data-splits.} This histogram shows the number of data-splits in each
bin. The percentage of dataplits where the difference between random
forest and L2-regularized logistic regression AUROC values was higher
than or equal to 0 were 0.75, lower than or equal to 0 were 0.25. The
vertical red line highlights the bins where there AUROC difference
between the two model is 0. The p-value was manually calculated using
the sampling distribution of the test statistic under the null
hypothesis. We are testing how often random forest performs more
accurately than L2-regularized logistic regression. We are assuming that
the distribution of the differences between the AUROC values of random
forest and L2 logistic regression is symmetric about 0, therefore we are
calculating the p-value for a double-tail event. \newpage
\includegraphics[height=17.5cm, width=13cm]{Figure_S4.png}

@@

\textbf{Figure S5. Interpretation of the linear ML models with
permutation importance.} (A) L1-regularized SVM with linear kernel, (B)
L2-regularized SVM with linear kernel, and (C) L2-regularized logistic
regression were interpreted using permutation importance using held-out
test set.

>>>>

ML models can be used to increase our understanding of the variation in
the structure of existing data and in making predictions about new data.
Researchers have used ML models to diagnose and understand the
ecological basis of diseases such as liver cirrhosis, colorectal cancer,
inflammatory bowel diseases, obesity, and type 2 diabetes (2--19). The
task of diagnosing an individual relies on a rigorously validated model.
However, there are common methodological and reporting problems that
arise when applying ML to such data, that need to be addressed for the
field to progress. These problems include a lack of transparency in
which methods are used and how these methods are implemented; evaluating
models without separate held-out test data; unreported variation between
the predictive performance on different folds of cross-validation; and
unreported variation between cross-validation and testing performances.
Though the microbiome field is making progress to avoid some of these
pitfalls including validating their models on independent datasets (8,
19, 20) and introducing accessible and open-source ML tools (21--24),
more work is needed to improve reproducibility further and minimize
overestimating for model performance.

@@

In this study, we provided steps toward standardization of machine
learning methods for microbiome studies which are often poorly
documented and executed. To showcase a rigorous ML pipeline and to shed
light on how ML model selection can affect modeling results, we
performed an empirical analysis comparing the predictive performance,
interpretability and training times of seven modeling approaches with
the same dataset and pipeline. We built three linear models with
different forms of regularization: L2-regularized logistic regression
and L1 and L2-regularized support vector machines (SVM) with a linear
kernel. We also trained four non-linear models: SVM with radial basis
function kernel, a decision tree, random forest, and gradient boosted
trees. We compared their predictive performance, interpretability, and
training time. To demonstrate the performance of these modeling
approaches and our pipeline on a case study, we used a data from a
previously published study that sought to classify individuals as having
healthy colons or colonic lesions based on the 16S rRNA gene sequences
collected from fecal samples (4). This dataset was selected because it
is a relatively large collection of individuals (N=490) connected to a
clinically significant disease where there is ample evidence that the
disease is driven by variation in the microbiome (2, 4, 5, 32). With
this dataset, we developed an ML pipeline that can be used in many
different scenarios for training and evaluating models. This framework
can be easily applied to other host-associated and environmental
microbiome datasets. We also provided an aspirational rubric for
evaluating the rigor of ML practices applied to microbiome data
{[}Figure S1{]} to urge the audience to be diligent with with their
study design, model selection, development, evaluation and
interpretation.

@@

First, we randomly split the data into training and test sets so that
the training set consisted of 80\% of the full dataset, while the test
set was composed of the remaining 20\% {[}Figure 1{]}. To maintain the
distribution of controls and cases found in the full dataset, we
performed stratified splits. For example, our full dataset included 490
individuals. Of these, 261 had healthy colons (53\%) and 229 had a
screen relevant neoplasia (SRN; 46.7\%). A training set included 393
individuals, of which 209 had an SRN (53\%), while the test set was
composed of 97 individuals, of which 52 had an SRN (54\%). The training
data were used to build and select the models, and the test set was used
for evaluating the model. We trained seven different models using the
training data {[}Table 1{]}.

@@

\textbf{Interpretation of each ML model.} To evaluate the overall
structure of the CRC dataset and show that the structure of the human
microbiome is remarkably variable among individuals with SRNs, we
analyzed the Bray-Curtis distances with an NMDS ordination {[}Figure
S5{]}. The lack of seperation between healthy patients and patients with
SRNs, show that traditional statistical approaches do not help us to
adequately address disease ecology. This is why we often use ML models
not just to predict a health outcome, but also to identify potential
biomarkers for disease. Therefore, model interpretation becomes crucial
for microbiome studies. Interpretability is related to the degree to
which humans can understand the reasons behind a model prediction
(33--35). ML models often decrease in interpretability as they increase
in complexity. In this study, we used two methods to help interpret our
models.

First, we interpreted the feature importance of the linear models (L1
and L2-regularized SVM with linear kernel and L2-regularized logistic
regression) using the median rank of absolute feature weights for each
OTU {[}Figure 3{]}. We also reviewed the signs of feature weights to
determine whether an OTU was associated with classifying a subject as
being healthy or having an SRN. It was encouraging that many of the
highest-ranked OTUs were shared across these three models (e.g., OTUs
50, 426, 609, 822, 1239). The great benefit of this approach was knowing
the sign and magnitude of each OTU coefficient in the trained model.
This allowed us to immidiately interpret negative and positive
coefficient signs as protective and risk factors, respectively and the
magnitude as the impact of these factors. However, this approach is
limited to linear models or models with prespecified interaction terms.

Second, to analyze non-linear models, we interpreted the feature
importance using permutation importance (36). Whereas the absolute
feature weights were determined from the trained models, here we
measured importance using the held-out test data. Permutation importance
analysis is a post hoc explanation of the model, in which we randomly
permuted groups of perfectly correlated features together and other
features individually across the two groups in the held-out test data
{[}Figure S6{]}. We then calculated how much the predictive performance
of the model (i.e., testing AUROC values) decreased when each OTU or
group of OTUs was randomly permuted. We ranked the OTUs based on how
much the median testing AUROC decreased when it was permuted; the OTU
with the largest decrease ranked highest {[}Figure 4{]}. Among the
twenty OTUs with the largest impact, there was only one OTU (OTU 822)
that was shared among all of the models; however, we found three OTUs
(OTUs 58, 110, 367) that were important in each of the tree-based
models. Similarly, the random forest and XGBoost models shared four of
the most important OTUs (OTUs 2, 12, 361, 477). Permutation analysis
results also revealed that with the exception of the decision tree
model, removal of any individual OTU had minimal impact on model
performance. For example, if OTU 367 was permuted across the samples in
the decision tree model, the median AUROC dropped from 0.601 to 0.525.
In contrast, if the same OTU was permuted in the random forest model,
the AUROC only dropped from 0.695 to 0.680, which indicated high degree
of collinearity in the dataset. Permutation analysis allowed us to gauge
the importance of each OTU in non-linear models and partially account
for collinearity by grouping correlated OTUs to determine their impact
as a group.

To further highlight the differences between the two interpretation
methods, we used permutation importance to interpret the linear models
{[}Figure S7{]}. When we analyzed the L1-regularized SVM with linear
kernel model using feature rankings based on weights {[}Figure 3{]} and
permutation importance {[}Figure S6{]}, 17 of the 20 top OTUs (e.g., OTU
609, 822, 1239) were deemed important by both interpretation methods.
Similarly, for the L2-regularized SVM and L2-regularized logistic
regression, 9 and 12 OTUs, respectively, were shared among the two
interpretation methods. These results indicate that both methods are
consistent in selecting the most important OTUs.

We also compared the top 20 OTUs selected by permutation importance in
L2-regularized logistic regression and the highest performing tree-based
models, random forest and XGBoost. 2 and 5 OTUs, respectively, were
shared among the models. These results indicate that we were able to
identify a few more OTUs that are deemed important by both linear and
non-linear models when we used permutation importance as our
interpretation method.

Figure S7:

@@

We highlighted the importance of model interpretation to gain greater
biological insights into microbiota-associated diseases. In this study,
we showcased two different interpretation methods: ranking each OTU by
(i) their absolute weights in the trained models and (ii) their impact
on the predictive performance based on permutation importance.
Human-associated microbial communities have complex correlation
structures that create collinearity in the datasets. This can hinder our
ability to reliably interpret models because the feature weights of
correlated OTUs are influenced by one another (37). To capture all
important features, once we identify highly ranked OTUs, we should
review their relationships with other OTUs. These relationships will
help us generate new hypotheses about the ecology of the disease and
test them with follow-up experiments. When we used permutation
importance, we partially accounted for collinearity by grouping
correlated OTUs to determine their impact as a group. We grouped OTUs
that had a perfect correlation with each other; however, we could reduce
the correlation threshold to further investigate the relationships among
correlated features. We are choosing to leave the decision to define
correlation and setting up correlations thresholds to the researchers
for their own microbiome questions. However, we would like to urge them
to investigate the correlation structures of the data to avoid
misinterpreting the models. This is likely to be a particular problem
with shotgun metagenomic datasets where collinearity will be more
pronounced due to many genes being correlated with one another because
they come from the same chromosome. True causal mechanisms (e.g., role
of microbiome in colorectal cancer) cannot be explained solely by the
highest performing machine learning model (38). To identify the true
underlying microbial factors of a disease, it is crucial to follow up on
any correlation analyses with further hypothesis testing and
experimentation for biological validation.

@@

\hypertarget{ref-miller_explanation_2017}{}
33. \textbf{Miller T}. 2017. Explanation in artificial intelligence:
Insights from the social sciences. arXiv:170607269 {[}cs{]}.

\hypertarget{ref-ribeiro_why_2016}{}
34. \textbf{Ribeiro MT}, \textbf{Singh S}, \textbf{Guestrin C}. 2016.
``Why should i trust you?'': Explaining the predictions of any
classifier. arXiv:160204938 {[}cs, stat{]}.

\hypertarget{ref-nori_interpretml:_2019}{}
35. \textbf{Nori H}, \textbf{Jenkins S}, \textbf{Koch P},
\textbf{Caruana R}. 2019. InterpretML: A unified framework for machine
learning interpretability. arXiv:190909223 {[}cs, stat{]}.

\hypertarget{ref-10.1093ux2fbioinformaticsux2fbtq134}{}
36. \textbf{Altmann A}, \textbf{Toloşi L}, \textbf{Sander O},
\textbf{Lengauer T}. 2010. Permutation importance: a corrected feature
importance measure. Bioinformatics \textbf{26}:1340--1347.
doi:\href{https://doi.org/10.1093/bioinformatics/btq134}{10.1093/bioinformatics/btq134}.

\hypertarget{ref-dormann_collinearity:_2013}{}
37. \textbf{Dormann CF}, \textbf{Elith J}, \textbf{Bacher S},
\textbf{Buchmann C}, \textbf{Carl G}, \textbf{Carré G}, \textbf{Marquéz
JRG}, \textbf{Gruber B}, \textbf{Lafourcade B}, \textbf{Leitão PJ},
\textbf{Münkemüller T}, \textbf{McClean C}, \textbf{Osborne PE},
\textbf{Reineking B}, \textbf{Schröder B}, \textbf{Skidmore AK},
\textbf{Zurell D}, \textbf{Lautenbach S}. 2013. Collinearity: A review
of methods to deal with it and a simulation study evaluating their
performance. Ecography \textbf{36}:27--46.
doi:\href{https://doi.org/10.1111/j.1600-0587.2012.07348.x}{10.1111/j.1600-0587.2012.07348.x}.

\hypertarget{ref-li_accurate_2020}{}
38. \textbf{Li J}, \textbf{Liu L}, \textbf{Le TD}, \textbf{Liu J}. 2020.
Accurate data-driven prediction does not mean high reproducibility. Nat
Mach Intell \textbf{2}:13--15.
doi:\href{https://doi.org/10.1038/s42256-019-0140-2}{10.1038/s42256-019-0140-2}.

@@

\textbf{Figure 4. Interpretation of the non-linear ML models.} (A) SVM
with radial basis kernel, (B) decision tree, (C) random forest, and (D)
XGBoost feature importances were explained using permutation importance
on the held-out test data set. The gray rectangle and the dashed line
show the IQR range and median of the base testing AUROC without any
permutation. The 20 OTUs that caused the largest decrease in the AUROC
when permuted are reported here. The colors of the box plots represent
the OTUs that were shared among the different models; yellow were OTUs
that were shared among all the non-linear models, green were OTUs that
were shared among the tree-based models, green were the OTUs shared
among SVM with radial basis kernel, decision tree and XGBoost, pink were
the OTUs shared among SVM with radial basis kernel and XGBoost only, red
were the OTUs shared among random forest and XGBoost only and blue were
the OTUs shared among decision tree and random forest only. For all of
the tree-based models, a \emph{Peptostreptococcus} species (OTU00367)
had the largest impact on predictive performance. \newpage
\includegraphics{Figure_5.png}

@@

\textbf{Figure S3. Histogram of AUROC differences between L2-regularized
logistic regression and random forest for each of the hundred
data-splits.} In 75\% of data-splits, the AUROC of random forest was
greater than that of L2-regularized logistic regression. The p-value was
manually calculated using the sampling distribution of the test
statistic under the null hypothesis. We tested how often random forest
performed more accurately than L2-regularized logistic regression. The
null hypothesis is that the distribution of the difference between the
AUROC values of random forest and L2 logistic regression is symmetric
about 0, therefore the p-value was calculated for a double-tail event.
\newpage
\includegraphics[height=17.5cm, width=13cm]{Figure_S4.png}

@@

\textbf{Figure S5. NMDS ordination with Bray-Curtis distances.}

\includegraphics[height=17.5cm, width=13cm]{Figure_S6.png}

\textbf{Figure S6. Permutation importance analysis.} Permutation
importance analysis measures the decrease in the predictive performance
of the model after we permute (A) a feature's or (B) a group of
correlated features' values, which breaks the relationship between the
feature and the actual outcome.

\includegraphics[height=17.5cm, width=13cm]{Figure_S7.png}

\textbf{Figure S7. Interpretation of the linear ML models with
permutation importance.} (A) L1-regularized SVM with linear kernel, (B)
L2-regularized SVM with linear kernel, and (C) L2-regularized logistic
regression were interpreted using permutation importance using held-out
test set.
